Article Title

### 2013-08-07 sections/Results.tex
added Figure 2: regularization target as graphical models.

\textbf{Figure 3.}{ 
The fitting performance of regularized covariance estimators on two-photon recording. 
}\label{fig:03}

\textbf{Figure 4.}{ 
Fitting performance of regularized covariance estimators on 24 datasets two-photon recordinngs.
}\label{fig:04}

\textbf{Figure 5.}{
The depiction of the 3D arrangement of the non-zero partial correlations between pairs of neurons.
}\label{fig:04}

>>>>

\textbf{Figure 4.}{ 
The fitting performance of regularized covariance estimators on two-photon recording. 
}\label{fig:04}

\textbf{Figure 5.}{ 
Fitting performance of regularized covariance estimators on 24 datasets two-photon recordinngs.
}\label{fig:05}

\textbf{Figure 6.}{
The depiction of the 3D arrangement of the non-zero partial correlations between pairs of neurons.
}\label{fig:06}

### 2013-08-07 sections/Theory.tex
added Figure 2: regularization target as graphical models.

\subsection{Regularized covariance estimates}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.

@@

>>>>

\subsection{Regularization of covariance estimates}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.

@@

\textbf{Figure 2.}{
Gaussian Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: The Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from pairwise interactions between 
\textbf{D}: A similar covariance matrix with sparse + low-rank inverse with 3 latent units.
}\label{fig:02}
